### 2015-04-21 paper.tex
Fix up author designations

{\Large \textbf\newline{Measurements on a 1:6 scale DOE Reference Model 2
cross-flow hydrokinetic turbine at transitional Reynolds numbers: Power production, 
near-wake dynamics, and blade support strut losses}}
\newline
% Insert author names, affiliations and corresponding author email (do not include 
% titles, positions, or degrees).
\\
Peter Bachant\textsuperscript{1,\Yinyang},
Martin Wosnik\textsuperscript{1,\Yinyang},
Budi Gunawan\textsuperscript{2,\textcurrency a},
Vincent Neary\textsuperscript{2,\ddag}
\\
\bigskip
\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham, NH, 
USA
\\
\bf{2} Water Power Technologies, Sandia National Laboratories, Albuquerque, NM, USA
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert
% symbol callouts after author names as necessary.
%
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
\Yinyang These authors contributed equally to this work.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as
% senior authorship.
\ddag These authors also contributed equally to this work.

% Current address notes
\textcurrency a Insert current address of first author with an address update
% \textcurrency b Insert current address of second author with an address update
% \textcurrency c Insert current address of third author with an address update

% Deceased author note
\dag Deceased

% Group/Consortium Author Note
\textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* CorrespondingAuthor@institute.edu

>>>>

{\Large \textbf\newline{Measurements on a 1:6 scale DOE Reference Model 2
cross-flow hydrokinetic turbine at transitional Reynolds numbers: Power production, 
near-wake dynamics, and blade support strut losses}}
\newline
% Insert author names, affiliations and corresponding author email (do not include 
% titles, positions, or degrees).
\\
Peter Bachant\textsuperscript{1,*},
Martin Wosnik\textsuperscript{1},
Budi Gunawan\textsuperscript{2},
Vincent Neary\textsuperscript{2}
\\
\bigskip
\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham, NH, 
USA
\\
\bf{2} Water Power Technologies, Sandia National Laboratories, Albuquerque, NM, USA
\\
\bigskip

% Use the asterisk to denote corresponding authorship and provide email address
% in note below.
* pxL3@unh.edu
